%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
\cventry
{Freelance Software Engineer} % Job title
{rViz Ltd.} % Organization
{Manchester UK - Remote} % Location
{Feb. 2023 - May 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Provided expert consultation on modern development practices and integrating Azure B2C and Active Directory.}
    \item {Guided architecture and technology decisions.}
    \item {Developed a robust application for efficient user management and PowerBI report assignment.}
    \item {React, Typescript, Node, Azure Functions, Azure B2C, Active Directory.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Senior Software Engineer} % Job title
{Qubisoft Pty Ltd} % Organization
{Melbourne, Australia - Remote} % Location
{Jan. 2021 - Nov. 2022} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Led the development of an application to handle price and capacity bidding for an Australian electricity market participant, improving bidding efficiency and saving staff time by automating previously partly manual processes.} 
    \item {React, Typescript, .NET Core Web API, C\#, and MySQL.}
    \item {Developed a serverless architecture application for a speed dating company, enabling online speed dating events for up to 20 people with features such as group video chats, event booking and payment, and match display.}
    \item {Azure Functions, Service Bus, B2C, React, Typescript, C\#, Twilio, and Stripe.}
    \item {Maintained and enhanced a hospitality industry stock management application using React and Django.}
    \item {Mentored junior engineers and contributed to architecture decisions in the team.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{Vald Performance} % Organization
{Brisbane, Australia} % Location
{Jul 2019 - Dec 2020} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {A flexible full stack role within a small engineering team in a rapidly growing start‑up, working with a distributed micro‑services architecture.}
    \item {Responsible for new training program functionality for a major product including web front end and supporting APIs.}
    \item {Key part of a multi disciplinary and international group managing the integration of a newly acquired product onto VALD systems, including implementing significant permissions system enhancement.}
    \item {Guided and supported junior engineers in their professional growth.}
    \item {Technologies: C\#, .NET Core, Typescript, React, Azure Table Storage (NoSQL), SQL Server, Redis, Terraform, Jenkins, Octopus.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Founder} % Job title
{Youniqify} % Organization
{Melbourne, Australia} % Location
{Aug. 2014 - Apr. 2016} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Building a flexible product customisation application for integration with small online retailers.}
    \item {Technologies: Typescript, React, Redux, Golang, Google Cloud Platform.} 
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Contract Developer} % Job title
{Bacco Wines} % Organization
{Melbourne, Australia \& LA, U.S.A} % Location
{Jun. 2017 - Jul. 2018} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Built a multi-platform mobile shopping app for a wine retailer.}
    \item {Technologies: Xamarin, C\#, .NET, MVVM, XAML, SQLite.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Contract Developer} % Job title
{Millie Savage Jewellery} % Organization
{Melbourne, Australia} % Location
{Jan. 2017 - Jul. 2018} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Built a multi-platform mobile shopping app for a wine retailer}
    \item {Technologies: JQuery, Javascript, HTML, CSS.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Developer} % Job title
{DST Bluedoor (now SS\&C)} % Organization
{Melbourne, Australia} % Location
{Sep 2012 - Dec 2017} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Working on the Bluedoor product, a third party superannuation, fund platform and wealth manager registry solution.}
    \item {Played a significant role in the development of Electronic Business Submission for a large UK client, dramatically reducing end user workload per case.}
    \item {Facilitated knowledge transfer to newly established Indian development office through on-site training and online support.}
    \item {Served as Technical Lead to cover paternity leave, ensuring seamless project continuation.}
    \item {Technologies: .NET Framework, VB.NET, SQL Server.}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
